SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-26 docs/questioning.tex
minor additions, changes

Requirements:
\begin{itemize}
\item {\bf Flexibility} We check if an approach
can be adjusted in order to detect different {\sc cia} categories.
\item {\bf Ease of use} We examine if the mechanism that
implements an approach is practical and can be easily adopted
by security experts.
\item {\bf Effectiveness} As long as we examine security
mechanisms that detect either attacks or defects,
the non-existence of false positive and negative alarms
is a reasonable requirement.
\item {\bf Efficiency} Finally, we examine
the computational overhead of the mechanisms that affect the experience of
a web user who actually uses the protected application.
\item {\bf Security} How resilient is the system to
attacks made to to circumvent it.
\end{itemize}
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}.

@@

\section{Analysis Dimensions}

@@

@@

\subsection{Detection Circumvention}

@@

@@

	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).

>>>>

Requirements:
\begin{itemize}
\item {\it Diagnostic Performance} As long
as we examine protection mechanisms that detect
attacks, the non-existence of false positive and
negative alarms is a reasonable requirement.
\item {\it Computational Performance} We examine
the overhead of the mechanisms
that affect the experience of a web user who actually
uses the protected application.
\item {\it Ease of use} We examine if the protection
mechanism is practical in terms of deployment
and can be easily adopted by security experts.
\item {\it Security} How resilient is the system to
attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus}
\item {\it Availability}
\end{itemize}

All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}.

@@

\section{Analysis Dimensions}
\label{sec:dimensions}

@@

\subsection{Security}

@@

@@

Both categories involve more than one subcategories.
For every subcategory we provide elements regarding
every dimension we described in
Section~\ref{sec:dimensions}.

@@

	based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic benchmarks ({\it s}), c) both ({\it a}).
